%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%Edited by Alexandre


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Added by me
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Print only mont and year
\usepackage{datetime}
\newdateformat{monthyeardate}{%
	\monthname[\THEMONTH], \THEYEAR}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Alexandre}{Ribeiro João Macedo}
\address{12 Boulevard des Maréchaux, Bâtiment Joffre, Studio 12.20.29 – 91120 Palaiseau, France}
\mobile{+33 06 67 26 57 04}
%
%%% Social
\email{arj.macedo@gmail.com}
\linkedin{alexandre-macedo}
%
%%% Personal
\nationality{Brazilian}
\birthday{21}{08}{1993}
%
%%% Optionals
%\statement{\textbf{Applying for an internship position from June 12\textsuperscript{th} to August 31\textsuperscript{st} 2017}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {}
  {\monthyeardate\today}
  {}

\begin{document}
%%% Make a header for CV with personal data
\makecvheader
%
%%% Entries
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Cycle d'ingénieur polytechnicien}
	{X- École Polytechnique}
	{Palaiseau, Île-de-France, France}
	{2015 - Present}
	{
		\begin{cvitems}
			\item{Studies in sciences and engineering: applied mathematics and computer sciences. Expected graduation in 2018.}
		\end{cvitems}
	}
	\cventry
	{B. S. Mechanical Engineering}
	{UFMG- Universidade Federal de Minas Gerais}
	{Belo Horizonte, MG, Brazil}
	{2012-2013; 2015}
	{
		\begin{cvitems}
			\item {4th year student. Graduation put on hold in the beginning of 2016.}
		\end{cvitems}
	}
	\cventry
	{Visiting student}
	{UofT- University of Toronto}
	{Toronto, ON, Canada}
	{2014}
	{
		\begin{cvitems}
			\item{Engineering studies: bioengineering and signal processing.}
		\end{cvitems}
	}
\end{cventries}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experiences
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Undergraduate research assistant}
	{morLAB/UofT- Medical Operations Research Laboratory}
	{Toronto, ON, Canada}
	{Summer 2014}
	{
		\begin{cvitems}
			\item {Acquired data for pandemic disease spread simulation model and did minor modifications on the model.}
		\end{cvitems}
	}
	\cventry
	{Undergraduate research assistant}
	{LRSS/UFMG- Laboratório de Robótica Soldagem e Simulação (Robotics,	Welding and Simulation Laboratory)}
	{Belo Horizonte, MG, Brazil \mbox{Oct. 2012 - Dec. 2013}}
	{}
	{
		\begin{cvitems}
			\item {Assited PhD students in preparing experiments for their thesis.}
		\end{cvitems}
	}
	\cventry
	{Teaching assistant}
	{Colégio Santo Antônio}
	{Belo Horizonte, MG, Brazil}
	{Mar. 2012 - Aug. 2013}
	{
		\begin{cvitems}
			\item {Assisted high school students by clarifying their questions in physics and mathematics.}
		\end{cvitems}
	}
\end{cventries}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Languages}
\begin{cvskills}
	\cvskill{Portuguese}{Native Speaker}
	\cvskill{English}{\makebox[2cm]{Fluent\hfill} TOEFL iBT (Dec. 2013): 103/120}
	\cvskill{French}{\makebox[2cm]{Advanced\hfill} TCF Compréhesion (Apr. 2016): C1}
\end{cvskills}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Computer Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Technical Skills}
\begin{cvskills}
	\cvskill{Programming}{Knowledgeable in MATLAB, Java, Python, C++}
	\cvskill{O.S.}{Linux, Windows}
	\cvskill{Other}{\LaTeX, Git, ROS}
\end{cvskills}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Volunteer Work}
\begin{cventries}
	\cventry
	{Teaching assistant}
	{GRUFAJE}
	{Belo Horizonte, MG, Brazil}
	{Aug. 2015 – Nov. 2015}
	{
		\begin{cvitems}
			\item{ Helped less fortunate students aging from 17 to 70 prepare for a high school validation test and university entry examinations.}
		\end{cvitems}
	}
\end{cventries}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Hobbies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Hobbies}
\begin{cvskills}
	\cvskill{Practicing Sports}{Tennis, Climbing, Judo, Sailing}
	\cvskill{Free Time}{Fishing, Watch movies}
\end{cvskills}
%
\end{document}